### 2016-07-29 ClimaTrans/climatrans.Rmd
Climatrans

```{r,echo=TRUE}
library(esd)
library(ncdf)
## Information about the system and session
sessionInfo()
```

@@

@@

Take hot events to be any day warmer than 30C:

```{r}
nhot <- annual(climatrans.tx,FUN='count',threshold=35)
plot(nhot,new=FALSE)
for(i in 1:3) lines(trend(subset(nhot,is=i)))
grid()
print(trend(nhot,result='pval')) 
```

@@

```{r}
  trh <- c(40,30,32)
  for (i in 1:3) {
    y <- subset(climatrans.tx,is=i)
    if (!file.exists(paste('dse.tx.climatrans.',loc(y),'.rda',sep=''))) {
      dse.tx <- DSensemble.t2m(y,biascorrect=TRUE,type='ncdf4',
                           predictor=predictor,nmin=60,verbose=FALSE)
      save(file=paste('dse.tx.climatrans.',loc(y),'.rda',sep=''),dse.tx)
    } else load(paste('dse.tx.climatrans.',loc(y),'.rda',sep=''))

    ## The function hotsummerdays estimates the number of hot days based on
    ## the assumption that the temperature is close to being normally distributed
    hw <- hotsummerdays(x=y,dse=dse.tx,threshold=trh[i],plot=TRUE,new=FALSE)
    #plot(hw)
  }
```

@@

@@

>>>>

```{r,echo=TRUE}
library(esd)
library(ncdf)
## Information about the system and session
```

@@

The function `hotsummerdays` is provided in `esd`, and the listing of the code is provided below:

```{r, eval=FALSE}
hotsummerdays <- function (x, y = NULL, dse = NULL, it = "jja", threshold = 30, 
    verbose = FALSE, plot = TRUE, nmin = 90, new = TRUE, ...) 
{
    if (verbose) 
        print("mildwinterdays")
    stopifnot(inherits(x, "station"))
    if (is.null(y)) 
        y <- x
    djf <- subset(x, it = it)
    djfy <- subset(y, it = it)
    nwd1 <- annual(djfy, FUN = "count", threshold = threshold, 
        nmin = nmin)
    mwd1 <- annual(djf, FUN = "mean", nmin = nmin)
    cal <- data.frame(x = c(coredata(mwd1)), y = c(coredata(nwd1)))
    dfit <- glm(y ~ x, family = "poisson", data = cal)
    if (plot) {
        if (new) 
            dev.new()
        par(bty = "n")
        plot(cal, pch = 19, ylim = c(0, 90), xlab = expression(paste("mean temperature ", 
            (degree * C))), ylab = "number of hot days", main = loc(x))
        pre <- data.frame(x = seq(min(cal$x, na.rm = TRUE) - 
            1, max(cal$x, na.rm = TRUE) + 5, by = 0.1))
        lines(pre$x, exp(predict(dfit, newdata = pre)), col = rgb(1, 
            0, 0, 0.3), lwd = 3)
        if (new) 
            dev.new()
        djf.sd <- sd(coredata(djf), na.rm = TRUE)
        qqnorm(coredata(djf))
        qqline(coredata(coredata(djf)), col = "red")
        grid()
    }
    if (is.null(dse)) 
        dse <- DSensemble.t2m(x, biascorrect = TRUE, verbose = verbose, 
            plot = plot)
    djf.dse <- subset(dse, it = "djf")
    index(djf.dse) <- year(djf.dse)
    ovl <- window(djf.dse, start = year(start(x)), end = year(end(x)))
    djf.dse <- djf.dse - mean(coredata(ovl), na.rm = TRUE) + 
        mean(coredata(mwd1), na.rm = TRUE)
    q1 <- data.frame(x = apply(coredata(djf.dse), 1, quantile, 
        probs = 0.05, na.rm = TRUE))
    q2 <- data.frame(x = apply(coredata(djf.dse), 1, quantile, 
        probs = 0.95, na.rm = TRUE))
    qm <- data.frame(x = apply(coredata(djf.dse), 1, mean, na.rm = TRUE))
    obs <- data.frame(x = coredata(mwd1))
    t <- year(index(djf.dse))
    preq1 <- exp(predict(dfit, newdata = q1))
    preq1[preq1 > 90] <- NA
    tr1 <- predict(lm(preq1 ~ t + I(t^2) + I(t^3) + I(t^4) + 
        I(t^5)))
    tr1[!is.finite(preq1)] <- NA
    preq2 <- exp(predict(dfit, newdata = q2))
    preq2[preq2 > 90] <- NA
    tr2 <- predict(lm(preq2 ~ t + I(t^2) + I(t^3) + I(t^4) + 
        I(t^5)))
    tr2[!is.finite(preq2)] <- NA
    prem <- exp(predict(dfit, newdata = qm))
    prem[prem > 90] <- NA
    tr3 <- predict(lm(prem ~ t + I(t^2) + I(t^3) + I(t^4) + I(t^5)))
    tr3[!is.finite(prem)] <- NA
    Nwd <- zoo(cbind(preq1, preq2, prem, tr1, tr2, tr3), order.by = t)
    nwd.pre <- zoo(exp(predict(dfit, newdata = obs)), order.by = year(mwd1))
    if (plot) {
        if (new) 
            dev.new()
        par(bty = "n")
        plot(zoo(djf.dse, order.by = year(djf.dse)), plot.type = "single", 
            col = rgb(0.5, 0.5, 0.5, 0.2), ylab = expression(paste("mean temperature", 
                (degree * C))), xlab = "", main = loc(x))
        points(mwd1, pch = 19)
        grid()
        if (new) 
            dev.new()
        par(bty = "n")
        plot(Nwd, plot.type = "single", lwd = 5, main = loc(x), 
            ylim = c(0, 90), xlab = "", ylab = paste("number of hot days: T(2m) > ", 
                threshold, unit(x)), col = c(rgb(0.5, 0.5, 0.7, 
                0.5), rgb(0.8, 0.5, 0.5, 0.5), rgb(0.8, 0.5, 
                0.8, 0.5), rgb(0.3, 0.3, 0.6, 0.5), rgb(0.6, 
                0.3, 0.3, 0.5), rgb(0.6, 0.3, 0.6, 0.5)), ...)
        grid()
        points(nwd1, pch = 19)
        lines(nwd.pre, col = rgb(0.5, 0.5, 0.5, 0.5))
    }
    Nwd <- attrcp(x, Nwd)
    attr(Nwd, "unit") <- "days"
    attr(Nwd, "info") <- paste("number of hot days: t2m > ", 
        threshold)
    attr(Nwd, "observation") <- nwd1
    attr(Nwd, "nwd.pre") <- nwd.pre
    index(Nwd) <- t
    class(Nwd) <- c("nevents", "zoo")
    invisible(Nwd)
}
```

@@

@@

```{r}
  trh <- c(40,35,35)
  for (i in 1:3) {
    y <- subset(climatrans.tx,is=i)
    if (!file.exists(paste('dse.tx.climatrans.',loc(y),'.rda',sep=''))) {
      dse.tx <- DSensemble.t2m(y,biascorrect=TRUE,type='ncdf4',
                           predictor=predictor,nmin=60,verbose=FALSE)
      save(file=paste('dse.tx.climatrans.',loc(y),'.rda',sep=''),dse.tx)
    } else load(paste('dse.tx.climatrans.',loc(y),'.rda',sep=''))

    ## The function hotsummerdays estimates the number of hot days based on
    ## the assumption that the temperature is close to being normally distributed
    dse.tx[is.element(year(dse.tx),2100),] <- NA   # some of the results for 2100 are suspect 
    hw <- hotsummerdays(x=y,dse=dse.tx,threshold=trh[i],it=NULL,plot=TRUE,new=FALSE)
    #plot(hw)
  }
```

@@

More traditional approaches of downscaling typically involve either downscaling daily data and estimate a probability density function (pdf) from these results or downscale the pdf directly in terms of the parameters describing the shape (<http://climatescience.oxfordre.com/view/10.1093/acrefore/9780190228620.001.0001/acrefore-9780190228620-e-27>). The probability of hot days may be estimated based on the pdf, and it is important to check the consistency between the data and the relevant parametric distribution.

@@

Take hot events to be any day warmer than 40C:

```{r}
for(i in 1:3) {
  nhot1 <- annual(subset(climatrans.tx,is=i),FUN='count',threshold=trh[i])
  if (i==1) nhot <- nhot1 else nhot <- combine(nhot,nhot1)
}
plot(nhot,new=FALSE)
for(i in 1:3) lines(trend(subset(nhot,is=i)))
grid()
print(trend(nhot,result='pval')) 
```
